### 2016-01-10 pdocs/thesis/introduction.tex
pdocs

>>>>

Software engineering is needed to implement suggested idea.

Few decades ago software engineering and structural analysis were highly coupled
and e.g. \cite{bathe} and \cite{cook} contain very detailed instructions on
computer implementation. Those books provided good baseline for many computer programs created in \lut for for analysis of 
thin-walled structures \cite{agifap,fsm,vtb}.

Getting and compiling complicated software packages is currently quite easy. 
Understanding and getting enough knowledge to extend them requires a fair amount of hard work.
